---
title: "Road Accidents Involving Cyclists"
author: "Jan Schubert"
date: "17 June 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
```

## About The Data

- This presentations shows a relationship between number of people cycling and number of road accidents involving a cyclist relative to the population.

- The data comes from the European Statistical Office.

## Road Accidents Involving Cyclists 
Countries above the line have higher than expected % of road accidents involving cyclists and vice versa

```{r cars}
library(plotly)
library(ggplot2)

cyclingData <- read.csv("cyclingData.csv")
cyclingData$once_a_day <- cyclingData$once_a_day*100 #convert to same units

p <- ggplot(data=cyclingData,aes(once_a_day,Pr_of_fatalities_cycling))+
    geom_point(alpha=0.75)+
    geom_smooth(method="lm",se = FALSE)+
    geom_text(aes(label=country),nudge_y=0.75,alpha=0.75)+
    xlab("% of people cycling at least once a day")+
    ylab("% of road fatalies involving a cyclist")+
    theme_classic()
ggplotly(p)
```